Population Inference of Non-Spinning Eccentric Binary Black Holes

### 2023-06-09 paper/paper.tex

Our first and second weighted populations with $\sigma_\epsilon=0.05, 0.1$ are given in \ref{fig:pop3d0.05_0.1}.

@@

\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.15.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.2.png}
\caption{\label{fig:pop3d0.15_0.2} Synthetic Population of EBBHs. The left figure represents the population for $\sigma_\epsilon=0.15$ and right figure represetns the population for $\sigma_\epsilon=0.2$}

@@

The first population is given in 
given in Fig. \ref{fig:pop3d05}.

@@

The second population is given in Fig. \ref{fig:pop3d038}.

We have the total $100$ events with a minimum and maximum primary mass of $15.12 M_\odot$ and $49.98 M_\odot$, respectively. Similarly, we have the secondary minimum and maximum masses $10.12 M_\odot$ and $46.01 M_\odot$ given in Fig \ref{fig:pop2d038}.

The second population is given in Fig. \ref{fig:pop3d038}.

Similarly, to get the non-eccentric population, we apply the Eq. \ref{eq:scaling} on the population given in Fig. \ref{fig:pop2d038} and get the new population with scaled masses. We get the new minimum and maximum values for the primary and secondary masses in Fig. \ref{fig:pop2d038scl}.

>>>>

Our weighted populations with $\sigma_\epsilon=0.05, 0.1$ and $\sigma_\epsilon=0.15, 0.2$ are given in Fig. \ref{fig:pop3d0.05_0.1} and Fig. \ref{fig:pop3d0.15_0.2} respectively.

\begin{table*}[]
    \centering
    \begin{tabular}{|ccccccc|}
        \hline
        $\sigma_\epsilon$ & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ & $\epsilon_{min}$ & $\epsilon_{max}$\\ \hline
        0.05 & 16.81 & 49.81 & 10.8 & 46.82 & 0.01 & 0.05\\ \hline
        0.1 & 19.03 & 49.93 & 10.1 & 48.64 & 0.05 & 0.1\\ \hline
        0.15 & 10.04 & 49.9 & 10.01 & 49.2 & 0.1 & 0.15\\ \hline
        0.2 & 19.6 & 49.97 & 10.73 & 48.39 & 0.15 & 0.2\\ \hline
    \end{tabular}
    \caption{Weighted Population Properties}
    \label{tab:pop_prop}
\end{table*}

@@

\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.15.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.2.png}
\caption{\label{fig:pop3d0.15_0.2} Synthetic Population of EBBHs. The left figure represents the population for $\sigma_\epsilon=0.15$ and right figure represents the population for $\sigma_\epsilon=0.2$}

@@

\begin{table*}[]
    \centering
    \begin{tabular}{|ccccccc|}
        \hline
        $\sigma_\epsilon$ & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ & $\epsilon_{min}$ & $\epsilon_{max}$\\ \hline
        0.05 & 16.68 & 49.64 & 10.77 & 46.75 & 0.01 & 0.05\\ \hline
        0.1 & 18.95 & 49.51 & 9.89 & 48.33 & 0.05 & 0.1\\ \hline
        0.15 & 9.13 & 49.55 & 9.1 & 49.11 & 0.1 & 0.15\\ \hline
        0.2 & 18.2 & 49.79 & 10.3 & 47.08 & 0.15 & 0.2\\ \hline
    \end{tabular}
    \caption{Scaled Population Properties}
    \label{tab:popscl_prop}
\end{table*}

@@
